ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python

### 2016-08-27 doc/paper.tex
out function doc
little fixes

When \autoref{lst:boilerplate} is run, an anonymous synth is created which will take in audio
from an external source, perform a STFT, process the spectral data with ScPy, perform an inverse
STFT, then finally output the resulting audio. Lines 8--9 contain Python code defining the
processing function where operations are to be inserted. Further examples will replace only those
lines. Line 16 contains the Python code to convert the spectrum into a NumPy array, process it,
then write back the processed version.

>>>>

When \autoref{lst:boilerplate} is run, an anonymous synth is created which will take in audio
from an external source, perform an STFT, process the spectral data with ScPy, perform an inverse
STFT, then finally output the resulting audio. Lines 8--9 contain Python code defining the
processing function where operations are to be inserted. Further examples will replace only those
lines. Line 16 contains the Python code to convert the spectrum into a NumPy array, process it,
then write back the processed version.

A special function, \texttt{out}, is provided to mutate data in SuperCollider buffers. It takes a
variable which is bound to a \texttt{Buffer} or \texttt{FFT} object and a new value. The buffer is
modified in place to hold the new data.
